```{r}
student<-read.csv('Q1a.csv',header=TRUE)
head(student)
```

QUESTION 1
a. Extract each dept students names separately
```{r}
aggregate(Name~Dept.Name,student,toString)
```

b. Extract S grade scores in all subjects in each dept seperately.
```{r}
s<-student[student$Sub1=="S"|student$Sub2=="S"|student$Sub3=="S"|student$Sub4=="S"|student$Sub5=="S", c("Name","Dept.Name")]

aggregate(Name~Dept.Name,s,toString)
```

c. Extract students who have scored at least S grades in any 2 subjects
```{r}
student[rowSums(student=="S")>1,c("Name","Dept.Name")]
```

d. Extract students who have scored above 9 SGPA in each dept
```{r}
s1<-student[student$SGPA>9,c("Name","Dept.Name")]
aggregate(Name~Dept.Name,s1,toString)

```
# now change all the grade value in each subject column to random marks and then execute these 2 querries
e.store numerical data and transform to grades and store in new data frame


```{r}
library(plyr)

student1 <-transform(student, Sub1=as.factor(mapvalues(Sub1,c(80:100,60:79,40:59,0:39),c(rep("A",21),rep("B",20),rep("C",20),rep("D",40)))))
student1


student2 <-transform(student1, Sub2=as.factor(mapvalues(Sub2,c(80:100,60:79,40:59,0:39),c(rep("A",21),rep("B",20),rep("C",20),rep("D",40)))))
student2


student3<-transform(student2, Sub3=as.factor(mapvalues(Sub3,c(80:100,60:79,40:59,0:39),c(rep("A",21),rep("B",20),rep("C",20),rep("D",40)))))
student3


student4 <-transform(student3, Sub4=as.factor(mapvalues(Sub4,c(80:100,60:79,40:59,0:39),c(rep("A",21),rep("B",20),rep("C",20),rep("D",40)))))
student4


student5 <-transform(student4, Sub5=as.factor(mapvalues(Sub5,c(80:100,60:79,40:59,0:39),c(rep("A",21),rep("B",20),rep("C",20),rep("D",40)))))
student5

```

f.check wether student grades are identical or not in each subject
```{r}
identical(student$Sub1,student$Sub2,student$Sub3,student$Sub4,student$Sub5)
```
```{r}
setequal(student$Sub1,student$Sub2)
```

