```{r}

s<-read.csv('Q7a.csv',header=TRUE)
s
```

a. Change the column names of Student data set. 
```{r}
colnames(s)<-c("Name","Stud_USN","Stud_Dept","S1","S2","S3","S4","S5","Stud_Grade","Stud_Gender","Stud_CGPA")
s
summary(s)

```

b. Use map values() , as.factor() and transform ()
c To change the Grade column(S,A,B,etc) to have numerical values. 1- S, 2-A,           3-B,etc.;
d To change gender column 1-Male, 2-Female
```{r}
library(plyr)
s<-transform(s,
             Stud_Grade=as.factor(mapvalues(Stud_Grade,c("S","A","B","C","D","E","F"),c(1,2,3,4,5,6,7))),
             Stud_Gender=as.factor(mapvalues(Stud_Gender,c("M","F"),c(1,2))))
s

```

e. Using with() and tapply() , calculate the mean of marks in each subject scored by students in each
department and mean of CGPA of students in each dept with respect to gender. Format it for markdown.
DONNO
```{r}
library(knitr)
library(rmarkdown)

kable(with(s,tapply(S1, INDEX = list(Stud_Dept,Stud_Gender),mean)),format="markdown")
kable(with(s,tapply(S2, INDEX = list(Stud_Dept,Stud_Gender),FUN=mean)),format="markdown")
kable(with(s,tapply(S3, INDEX = list(Stud_Dept,Stud_Gender),FUN=mean)),format="markdown")
kable(with(s,tapply(S4, INDEX = list(Stud_Dept,Stud_Gender),FUN=mean)),format="markdown")
kable(with(s,tapply(S5, INDEX = list(Stud_Dept,Stud_Gender),FUN=mean)),format="markdown")

kable(with(s,tapply(Stud_CGPA, INDEX = list(Stud_Dept,Stud_Gender), FUN=mean)),format="markdown")
```

f.Using with() and aggregate() , calculate the mean of marks in each subject scored by students in each department and the gender of students in each dept. Format it for markdown.
```{r}
kable(with(s,aggregate(S1,by=list(Stud_Dept,Stud_Gender),FUN=mean)),format="markdown")
kable(with(s,aggregate(S2,by=list(Stud_Dept,Stud_Gender),FUN=mean)),format="markdown")
kable(with(s,aggregate(S3,by=list(Stud_Dept,Stud_Gender),FUN=mean)),format="markdown")
kable(with(s,aggregate(S4,by=list(Stud_Dept,Stud_Gender),FUN=mean)),format="markdown")
kable(with(s,aggregate(S5,by=list(Stud_Dept,Stud_Gender),FUN=mean)),format="markdown")

```

