```{r}
faculty<-read.csv('Q1b.csv',header=TRUE)
head(faculty)
```

a. extract each dept faculty details separately
```{r}
aggregate(Name~Dept,faculty,toString)
```

b. extract Professors of each dept seperately
```{r}
prof<-faculty[faculty$Designation=="Professor",c("Name","Dept")]
aggregate(Name~Dept,prof,toString)
```

c. extract people who earn more than 1.5 lakh in each dept where their designation is prof,associate or assistant
```{r}
ppl<-faculty[faculty$Salary>150000,c("Name","Dept")]
aggregate(Name~Dept,ppl,toString)
```

d.Find out the cost of professors in each dept .(sum up their salary to get cost of them)
```{r}
prof<-faculty[faculty$Designation=="Professor",]
aggregate(Salary~Dept,prof,sum)
```

e. Find the cost of each dept faculty and average cost of faculty 
```{r}
cost<-aggregate(Salary~Dept,faculty,sum)
cost
avg_cost<-aggregate(Salary~Dept,faculty,mean)
avg_cost
```


f.Which dept has highest average and lowest  cost of faculty
```{r}
#highest average 
highavg_sal<-aggregate(Salary~Dept,faculty,mean)
highavg_sal[which.max(highavg_sal$Salary),]
#lowest cost
lowval<-aggregate(Salary~Dept,faculty,mean)
lowval[which.min(lowval$Salary),]
```



