```{r}
student<-read.csv('Q4a.csv',header = TRUE)
head(student)

```

a. Plot , in each dept, how many students have scored above 9 SGPA
```{r}
s<-student[student$SGPA>9,c("Name","Dept.Name")]
s
plot(s$Dept.Name)

```

b. Create subset of students , who have scored S grade in any subject and failed in any subject.
```{r}
sub<-subset(student,rowSums(student=="S")>=1 & rowSums(student=="F")>=1)
sub
```

c.Find out average SGPA of each dept students and Find out average score of each subject for each dept.
```{r}
#avg SGPA
aggregate(SGPA~Dept.Name,student,mean)
#avg score of each sub
aggregate(as.numeric(Sub1)~Dept.Name,student,mean)
```

d. Extract 10 toppers of each dept.
```{r}

s<-student[order(-student$SGPA),]

b<-s[s$Dept.Name=="BT",]
qb<-data.frame(b[1:10,c("Name","Dept.Name","SGPA")])
qb
cs<-s[s$Dept.Name=="CSE",]
qcs<-data.frame(cs[1:10,c("Name","Dept.Name","SGPA")])
qcs
e<-s[s$Dept.Name=="ECE",]
qe<-data.frame(e[1:10,c("Name","Dept.Name","SGPA")])
qe

```
e. Sort students details of each dept separately.
```{r}
student[order(student$Dept.Name,student$Name),]
```

f.Search for a particular student name in the data set, and retrieve his/her details
```{r}
subset(student,Name=="Aravind")
```

