```{r}
faculty<-read.csv('Q3a.csv',header=TRUE)
head(faculty)
```

a. Plot, in each dept, how many faculty are earning more than 1 lakh.
```{r}
f<-faculty[faculty$Salary>100000,c("Name","Dept")]
f
plot(f$Dept)

```

b. create subset of faculty, who have published more than 10 papers and their designation is Associate professor.
```{r}
sub<-subset(faculty,Designation=="Assosciate Professor" & Papers.Published>4)
sub
```

c. Find out average papers published by each dept, designation wise and Find out Average training programs attended by faculty each dept wise.
```{r}
#avg papers
aggregate(Papers.Published~Dept+Designation,faculty,mean)
#avg training 
aggregate(Training~Dept,faculty,mean)
```

d. Extract top 3 performers among faculty dept wise(more papers published and more training programmes attended)
```{r}
f<-faculty[order(-faculty$Papers.Published+-faculty$Training),]

cs<-f[f$Dept=="CSE",]
fq<-data.frame(cs[1:3,c("Name","Dept","Training","Papers.Published")])
fq

is<-f[f$Dept=="ISE",]
iq<-data.frame(is[1:3,c("Name","Dept","Training","Papers.Published")])
iq

```

e. Sort faculty details , dept wise separately
```{r}
faculty[order(faculty$Dept,faculty$Name),]

```

f. Search for faculty name in the data set and retrive his/her details
```{r}
subset(faculty,Name=="Mithra")

```

