#QUESTION 9 till e 

```{r}
f<-read.csv('Q5a.csv',header=TRUE)
f
```

a. Change the column names of faculty data set. 
```{r}
colnames(f)<-c("Names","Desig","Sal","Department","Trainings","Papers","Gender")
f
#summary(f)

```

b. Use map values() , as.factor() and transform ()
   -- to change the designation column to have numerical values. 1- Prof, 2-Asso.Prof,          3-Asst.Prof;
   --to change gender column 1-Male, 2-Female
```{r}
library(plyr)
f<-transform(f,
             Desig=as.factor(mapvalues(Desig,c("Professor","Assosciate Professor","Assistant Professor"),c(1,2,3))),
             Gender=as.factor(mapvalues(Gender,c("M","F"),c(1,2))))
f

```

c. Using with() and tapply() , calculate the mean training programs attended and no. of papers published in each department. Format it for markdown.
DONT KNOW
```{r}
library(knitr)
library(rmarkdown)

kable(with(f,tapply(Trainings,INDEX=list(Department,Papers),mean)),format="markdown")

```

d. Using with() and aggregate() , calculate the mean training programs attended and no. of papers published in each department. Format it for markdown.
```{r}
library(knitr)
library(rmarkdown)

kable(with(f,aggregate(Trainings,by=list(Department,Papers),mean)),format="markdown")

```

e. Check whether the mean value of no. of papers published in depts. are influenced by training programs attended and designation. Do regression analysis using aggregate().
```{r}
aggregate(Papers~Trainings+Desig,f,mean)

```



# QUESTION 10 


a. Create the table output for designation and papers published. Use with() and table().
```{r}
ans<-with(f,table(Papers,Desig))
ans 
```

b. Find the odds of lower no. of paper published with respect to designation and no.of training programs attended using the output of question (f).
DONNO
```{r}
ans.or<-as.numeric(ans[1,1])/as.numeric(ans[1,2])/as.numeric(ans[1,3])/as.numeric(ans[2,1])/as.numeric(ans[2,2])/as.numeric(ans[2,3])/as.numeric(ans[3,1])/as.numeric(ans[3,2])/as.numeric(ans[3,3])/as.numeric(ans[4,1])/as.numeric(ans[4,2])/as.numeric(ans[4,3])/as.numeric(ans[5,1])/as.numeric(ans[5,2])/as.numeric(ans[5,3])/as.numeric(ans[6,1])/as.numeric(ans[6,2])/as.numeric(ans[6,3])
ans.or
```

c. Is the designation affects the training programs attended? Check it with the data. Prove it.
```{r}
with(f,cor(as.numeric(Desig), Trainings))

```

d. Find the correlation of papers published and training programs attended using with(), cor().
```{r}
with(f,cor(Papers, Trainings))
```

e. Find the correlation of training programs attended and designation using with(), cor().
```{r}
with(f,cor(Trainings,as.numeric(Desig)))
```

f. Using by() combine the operations of above questions (i) and (j) using function. And do the correlation analysis using cor() with in the function.
```{r}
by(data = f[c("Papers", "Trainings")], 
   INDICES = f["Desig"], 
   FUN = function(x) {cor(x[,1], x[,2])})

```



#QUESTION 11


a. Plot average training programs attended against designations(only 3 designations) of the institution using plot()

```{r}
f1<-aggregate(Trainings~Desig,f,mean)
plot(f1$Desig, f1$Trainings)
```

b. Plot average papers published against designations of the institution using plot().

```{r}
f2<-aggregate(Papers~Desig,f,mean)
f2
plot(f2$Desig, f2$Papers)
```

c. Change the x axis , color and y-axis labels respectively. Add legends.
```{r}
# plot(f2$Desig, f2$Papers,xlab="Designation",ylab="Papers Published",main="Designation vs Papers Published",col=5)

par(mfrow = c(1,2))
with(f, plot(Desig, Trainings, 
                   main = "Designation vs Trainings", 
                   xlab = "Designation", 
                   ylab = "Tranings",col=7))
with(f, plot(Desig, Papers, 
                   main = "Designation vs Papers Published", 
                   xlab = "Designation", 
                    ylab = "Papers Published ",col=f$Desig))
legend("bottomright", c("Professor","Associate","Assistant"), col=c(1,2,3),pch=12)

```

d. Plot the above graphs in (l) and (m) using with() and plot().
```{r}
par(mfrow = c(1,2))
with(f, plot(Desig, Trainings, 
                   main = "Designation vs Trainings", 
                   xlab = "Designation", 
                   ylab = "Tranings",col=7))
with(f, plot(Desig, Papers, 
                   main = "Designation vs Papers Published", 
                   xlab = "Designation", 
                    ylab = "Papers Published ",col=8))


```

e. Draw scatter plot for above questions. Draw box plot for above question. Draw bar plots for above questions. Draw single variable plots for above question.
```{r}
par(mfrow = c(1,2))
with(f, plot(as.numeric(Desig), Trainings,
                   main = "Designation vs Trainings",
                   xlab = "Designation",
                   ylab = "Tranings",col=1))
with(f, plot(as.numeric(Desig), Papers,
                   main = "Designation vs Papers Published",
                   xlab = "Designation",
                    ylab = "Papers Published ",col=2))

par(mfrow = c(1,2))
with(f, boxplot(as.numeric(Desig), Trainings, 
                   main = "Designation vs Trainings", 
                   xlab = "Designation", 
                   ylab = "Tranings",col=1))
with(f, boxplot(as.numeric(Desig), Papers, 
                   main = "Designation vs Papers Published", 
                   xlab = "Designation", 
                    ylab = "Papers Published ",col=2))

par(mfrow = c(1,2))
with(f, barplot(as.numeric(Desig), Trainings, 
                   main = "Designation vs Trainings", 
                   xlab = "Designation", 
                   ylab = "Tranings",col=1))
with(f, barplot(as.numeric(Desig), Papers, 
                   main = "Designation vs Papers Published", 
                   xlab = "Designation", 
                    ylab = "Papers Published ",col=2))

```





```{r}

with(f,plot(Trainings))

```

f.plot the prof, asst.prof and asso.prof average performance in different colors using rep(), colorpalatte functions. Represent each designation average performance(no.of.papers published and training pgms atteneded) by different symbols.

```{r}
c1<-subset(f,Desig=="Assosciate Professor",c("Papers","Trainings"))
y1<-mean(c1$Papers+ c1$Trainings)
c2<-subset(f,Desig=="Assistant Professor",c("Papers","Trainings"))
y2<-mean(c2$Papers+c1$Trainings)
c3<-subset(f,Desig=="Professor",c("Papers","Trainings"))
y3<-mean(c3$Papers+c3$Trainings)
x<-c(1,2,3)
y<-c(y1,y2,y3)


p<-c(19,23,15)
 plot(x, y, main = "avg performance", 
                   xlab = "assoc prof", 
                   ylab = "Tranings",col=palette(),pch=p)
 
 with(f,text( x =1 ,y=y1, labels ="assoc prof",
                pos = rep(c(1, 3, 1), c(5, 1, 2)))) 


  with(f,text(x =2,y=y2, labels ="assis prof",
                pos = rep(c(1, 3, 1), c(5, 1, 2)))) 
  with(f,text(x =3,y=y3, labels ="prof",
                pos = rep(c(1, 3, 1), c(5, 1, 2)))) 

```

